Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-22 paper/current/main.tex
add missing citation bracket

This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring
Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
for example, organizations with a small L2 norm tend to also have a lower number of connections given their size (Fig.~\ref{fig:length}b, inset, $R^{2} = 0.17$). 
Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions. 
At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space. 
Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.

>>>>

This pattern has been observed in applications of neural embedding to natural language, wherein the length of word vectors were found to represent word "significance"~\autocite{schakel2015measuring}
Here, interpret the vector length instead as a measure of an organization's connectedness to other organizations given its size, where a connection is defined as a non-zero flow between organizations.
for example, organizations with a small L2 norm tend to also have a lower number of connections given their size (Fig.~\ref{fig:length}b, inset, $R^{2} = 0.17$). 
Large and prestigious universities can be considered as having a shorter vector length than expected given their size, reflecting their ability to attract researchers from many places, to place graduates in positions around the world, and the capacity to encourage mobility by offering temporary and visiting researcher positions. 
At the national level, the relative position of the convex-curves can reveal characteristics of their scientific organizations—for example, compared to the United States, Chinese organizations have a longer typical vector length (Fig.~\ref{fig:length}b) reflecting lower overall connectedness in the embedding space. 
Prestige is a key component academic mobility—by encoding information relating to prestige, neural embeddings offer a means of better representing functional distance between organizations and capturing the global landscape of mobility.
